SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-07 back.tex
minor

%% Simple stride prefetching techniques only detect sequences of addresses that differ by a constant value and fail to capture diverse memory access patterns. 
Lookahead prefetchers can learn complicated patterns by collecting histories of
observed data access patterns.
%EB: Didn't really understand this: 
%% "and correlating these with the strides, by considering each new page in a vacuum."
Kim {\em et. al.} proposed
SPP~\cite{SPP}, a confidence-based lookahead prefetcher. SPP creates a
signature associated to a memory request by compressing the history of
accesses. By correlating the signature with future likely delta patterns, SPP
learn both simple and complicated memory access patterns quickly. Our proposed
technique builds upon SPP. Thus, we describe SPP in more detail.

>>>>

%% Simple stride prefetching techniques only detect sequences of
%% addresses that differ by a constant value and fail to capture
%% diverse memory access patterns.
Lookahead prefetchers can learn complicated patterns by collecting
histories of observed data access patterns.
%EB: Didn't really understand this: 
%% "and correlating these with the strides, by considering each new
%% page in a vacuum."
Kim {\em et. al.} proposed SPP~\cite{SPP}, a confidence-based
lookahead prefetcher.  SPP creates a per-page signature by compressing
the history of recent accesses to a given page.  By correlating the
signature with future likely access patterns, SPP learn both simple
and complicated memory access patterns quickly.  Our proposed
technique builds upon SPP. Thus, we describe SPP in more detail.
